Code Club Project: Assessing whether intra and inter-genomic variation hinder utility of ESVs and ASVs

### 2020-12-22 submission/manuscript.Rmd
Create title page

@@

>>>>

---
output:
  word_document: default
  pdf_document:
    keep_tex: true
geometry: margin=1.0in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
---

# Amplicon sequence variants should not replace operational taxonomic units in marker-gene data analysis

\vspace{20mm}

**Running title:** ASVs vs. OTUs

\vspace{20mm}

Patrick D. Schloss${^\dagger}$

\vspace{40mm}

${\dagger}$ To whom corresponsdence should be addressed:

\href{mailto:pschloss@umich.edu}{pschloss@umich.edu}

Department of Microbiology & Immunology

University of Michigan

Ann Arbor, MI 48109

\vspace{20mm}

**Observation Format**

\newpage

@@

\newpage
